---
title: "Fall 2019 Report"
author: "Jacob Samuels"
date: "1/2/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
library(readr)
library(dplyr)
Fall <- read_csv("~/UCLA Baseball/Fall 2019/Fall 2019 All Games (Complete Dataset-Adj. for BIP).csv")

source("Swing and Contact Rates.R")
```

# Adrian Chaidez:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Chaidez, Adrian", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Chaidez, Adrian", Fall)
```

# Daniel Colwell:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Colwell, Daniel", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Colwell, Daniel", Fall)
```

\pagebreak

# Jack Filby:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Filby, Jack", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Filby, Jack", Fall)
```

# Josh Hahn:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Hahn, Josh", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Hahn, Josh", Fall)
```

\pagebreak

# Charles Harrison:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Harrison, Charles", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Harrison, Charles", Fall)
```

# Jared Karros:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Karros, Jared", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Karros, Jared", Fall)
```

\pagebreak

# Kyle Mora:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Mora, Kyle", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Mora, Kyle", Fall)
```

# Sean Mullen:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Mullen, Sean", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Mullen, Sean", Fall)
```

\pagebreak

# Nick Nastrini:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Nastrini, Nick", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Nastrini, Nick", Fall)
```

# Zach Pettway:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Pettway, Zack", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Pettway, Zack", Fall)
```

\pagebreak

# Holden Powell:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Powell, Holden", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Powell, Holden", Fall)
```

# Felix Rubi:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Rubi, Felix", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Rubi, Felix", Fall)
```

\pagebreak

# Jake Saum:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Saum, Jake", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Saum, Jake", Fall)
```

# Nick Scheidler:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Scheidler, Nick", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Scheidler, Nick", Fall)
```

\pagebreak

# Michael Townsend:

## Swing Rates:
```{r, echo=FALSE}
swing_rate("Townsend, Michael", Fall)
```

## Contact Rates:
```{r, echo=FALSE}
contact_rate("Townsend, Michael", Fall)
```

