---
title: "TrackMan UCI Data"
author: "Jacob Samuels"
date: "11/9/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
library(readr)
library(dplyr)
Umpire1 <- read_csv("~/UCLA Baseball/CSVs/2021 Winter/Jan-Feb2021.csv", skip = 3)
Umpire <- Umpire1 %>% filter(PitchCall != "BallIntentional") %>% filter(!is.na(PlateLocSide))
```

```{r, echo=FALSE, include=FALSE}
TM1 <- Umpire[,c(22,41,42)]
table(is.na(TM1))
names(TM1) <- c("PitchCall", "PlateLocHeight", "PlateLocSide")
#View(TM1)
```

```{r, echo=FALSE, include=FALSE}
Ump1L <- Umpire[which(Umpire$BatterSide == "Left"),]
Ump1R <- Umpire[which(Umpire$BatterSide == "Right"),]
TM1L <- Ump1L[,c(22,41,42)]
TM1R <- Ump1R[,c(22,41,42)]
```

#Umpire vs. LHH

```{r, echo=FALSE, include=FALSE}
table(is.na(TM1L))
names(TM1L) <- c("PitchCall", "PlateLocHeight", "PlateLocSide")
#View(TM1L)
```

```{r, echo=FALSE, include=FALSE}
TM1L$High <- rep(0, nrow(TM1L))
TM1L$Low <- rep(0, nrow(TM1L))
TM1L$Lefty <- rep(0, nrow(TM1L))
TM1L$Righty <- rep(0, nrow(TM1L))
TM1L$StrikeZone <- rep(0, nrow(TM1L))
TM1L$CloseK <- rep(0, nrow(TM1L))
TM1L$CloseB <- rep(0, nrow(TM1L))
TM1L$CloseH <- rep(0, nrow(TM1L))
for (i in 1:nrow(TM1L)) {
  TM1L$High[i] <- ifelse(TM1L$PlateLocHeight[i] > 3.5, 1, 0)
  TM1L$Low[i] <- ifelse(TM1L$PlateLocHeight[i] < 1.5, 1, 0)
  TM1L$Lefty[i] <- ifelse(TM1L$PlateLocSide[i] < -0.8333333, 1, 0)
  TM1L$Righty[i] <- ifelse(TM1L$PlateLocSide[i] > 0.8333333, 1, 0)
  TM1L$StrikeZone[i] <- ifelse(TM1L$High[i] == 0 && TM1L$Low[i] == 0 && TM1L$Lefty[i] == 0 && TM1L$Righty[i] == 0, 1, 0)
  if(0.5 < TM1L$PlateLocSide[i] && TM1L$PlateLocSide[i] < 0.8333333) TM1L$CloseK[i] <- 1
  if(-0.5 > TM1L$PlateLocSide[i] && TM1L$PlateLocSide[i] > -0.8333333) TM1L$CloseK[i] <- 1
  if(0.8333333 < TM1L$PlateLocSide[i] && TM1L$PlateLocSide[i] < 1.1) TM1L$CloseB[i] <- 1
  if(-0.8333333 > TM1L$PlateLocSide[i] && TM1L$PlateLocSide[i] > -1.1) TM1L$CloseB[i] <- 1
  if(1 < TM1L$PlateLocHeight[i] && TM1L$PlateLocHeight[i] < 4) TM1L$CloseH[i] <- 1
}
```

```{r, echo=FALSE, include=FALSE}
TM1L$KcalledB <- rep(0, nrow(TM1L))
TM1L$BcalledK <- rep(0, nrow(TM1L))
TM1L$KcalledK <- rep(0, nrow(TM1L))
TM1L$BcalledB <- rep(0, nrow(TM1L))
TM1L$Incorrect <- rep(0, nrow(TM1L))
TM1L$Correct <- rep(0, nrow(TM1L))
for (i in 1:nrow(TM1L)) {
  TM1L$KcalledB[i] <- ifelse(TM1L$StrikeZone[i] == 1 && TM1L$PitchCall[i] == "BallCalled", 1, 0)
  TM1L$BcalledK[i] <- ifelse(TM1L$StrikeZone[i] == 0 && TM1L$PitchCall[i] == "StrikeCalled", 1, 0)
  TM1L$KcalledK[i] <- ifelse(TM1L$StrikeZone[i] == 1 && TM1L$PitchCall[i] == "StrikeCalled", 1, 0)
  TM1L$BcalledB[i] <- ifelse(TM1L$StrikeZone[i] == 0 && TM1L$PitchCall[i] == "BallCalled", 1, 0)
  if(TM1L$KcalledB[i] == 1) TM1L$Incorrect[i] <- 1
  if(TM1L$BcalledK[i] == 1) TM1L$Incorrect[i] <- 1
  if(TM1L$KcalledK[i] == 1) TM1L$Correct[i] <- 1
  if(TM1L$BcalledB[i] == 1) TM1L$Correct[i] <- 1
}
```

```{r, echo=FALSE, include=FALSE}
KBsum <- sum(TM1L$KcalledB)
BKsum <- sum(TM1L$BcalledK)
KKsum <- sum(TM1L$KcalledK)
BBsum <- sum(TM1L$BcalledB)
accurate <- KKsum + BBsum
inaccurate <- KBsum + BKsum
strikes <- KBsum + KKsum
balls <- BKsum + BBsum
accurate
inaccurate
total <- accurate + inaccurate
umpire <- matrix(c(KBsum, BKsum, inaccurate, (KKsum), BBsum, accurate, strikes, balls, total, round(KKsum/strikes, 3), round(BBsum/balls, 3), round(accurate/total, 3)), ncol = 3, byrow = TRUE)
colnames(umpire) <- c("Zone", "No Zone", "Total")
rownames(umpire) <- c("Incorrect", "Correct", "Total", "Accuracy")
```

Table showing umpire's accuracy:

```{r, echo=FALSE}
umpire
```

```{r, echo=FALSE, include=FALSE}
thislist <- 0
thislist2 <- 0
thislist3 <- 0
thislist4 <- 0
thislist5 <- 0
thislist6 <- 0
for (i in 1:nrow(TM1L)) {
  if(TM1L$Incorrect[i] == 1) thislist <- c(thislist, i)
  if(TM1L$KcalledB[i] == 1) thislist2 <- c(thislist2, i)
  if(TM1L$BcalledK[i] == 1) thislist3 <- c(thislist3, i)
  if(TM1L$Correct[i] == 1) thislist4 <- c(thislist4, i)
  if(TM1L$CloseK[i] == 1 && TM1L$KcalledK[i] == 1 && TM1L$CloseH[i] == 1) thislist5 <- c(thislist5, i)
  if(TM1L$CloseB[i] == 1 && TM1L$Correct[i] == 1 && TM1L$CloseH[i] == 1) thislist6 <- c(thislist6, i)
}
TMWrong <- TM1L[thislist[-1],]
TMKcalledB <- TM1L[thislist2[-1],]
TMBcalledK <- TM1L[thislist3[-1],]
TMCorrect <- TM1L[thislist4[-1],]
TMCloseK <- TM1L[thislist5[-1],]
TMCloseB <- TM1L[thislist6[-1],]
nrow(TMWrong)
nrow(TMKcalledB)
nrow(TMBcalledK)
nrow(TMCorrect)
nrow(TMCloseK)
nrow(TMCloseB)
```

```{r, echo=FALSE}
library(ggplot2)
ggplot(data = TMKcalledB, aes(PlateLocSide*-1, PlateLocHeight)) + geom_point(color = "orange") + geom_point(data = TMBcalledK, aes(PlateLocSide*-1, PlateLocHeight), color = "red") + geom_point(data = TMCloseK, aes(PlateLocSide*-1, PlateLocHeight), color = "blue") + geom_point(data = TMCloseB, aes(PlateLocSide*-1, PlateLocHeight), color = "green") + geom_vline(xintercept = -0.8333333) + geom_vline(xintercept = 0.8333333) + geom_hline(yintercept = 3.5) + geom_hline(yintercept = 1.5) + ggtitle("Behind Home View of Umpire's Close Calls") + xlab("") + ylab("") + theme(plot.title = element_text(hjust = 0.5))
```

```{r, echo=FALSE, include=FALSE}
#View(TMWrong)
thislist2 <- 0
for (i in 1:nrow(TMWrong)) {
  if(TMWrong$StrikeZone[i] == 0) thislist2 <- c(thislist2, i)
}
TMBalls <- TMWrong[thislist2[-1],]
#View(TMBalls)
missareaprop <- prop.table(c(sum(TMBalls$High), sum(TMBalls$Low), sum(TMBalls$Lefty), sum(TMBalls$Righty)))
missarea <- matrix(c(sum(TMBalls$High), sum(TMBalls$Low), sum(TMBalls$Lefty), sum(TMBalls$Righty), sum(c(TMBalls$High, TMBalls$Low, TMBalls$Lefty, TMBalls$Righty)), round(missareaprop[1], 3), round(missareaprop[2], 3), round(missareaprop[3], 3), round(missareaprop[4], 3), 1), nrow = 2, byrow = TRUE)
colnames(missarea) <- c("Up", "Down", "Lefty In", "Lefty Out", "Total")
rownames(missarea) <- c("Misses", "Proportion")
```

Location of missed calls:

```{r, echo=FALSE}
missarea
```

\pagebreak

# Umpire vs. RHH

```{r, echo=FALSE, include=FALSE}
table(is.na(TM1R))
names(TM1R) <- c("PitchCall", "PlateLocHeight", "PlateLocSide")
#View(TM1R)
```

```{r, echo=FALSE, include=FALSE}
TM1R$High <- rep(0, nrow(TM1R))
TM1R$Low <- rep(0, nrow(TM1R))
TM1R$Lefty <- rep(0, nrow(TM1R))
TM1R$Righty <- rep(0, nrow(TM1R))
TM1R$StrikeZone <- rep(0, nrow(TM1R))
TM1R$CloseK <- rep(0, nrow(TM1R))
TM1R$CloseB <- rep(0, nrow(TM1R))
TM1R$CloseH <- rep(0, nrow(TM1R))
for (i in 1:nrow(TM1R)) {
  TM1R$High[i] <- ifelse(TM1R$PlateLocHeight[i] > 3.5, 1, 0)
  TM1R$Low[i] <- ifelse(TM1R$PlateLocHeight[i] < 1.5, 1, 0)
  TM1R$Lefty[i] <- ifelse(TM1R$PlateLocSide[i] < -0.8333333, 1, 0)
  TM1R$Righty[i] <- ifelse(TM1R$PlateLocSide[i] > 0.8333333, 1, 0)
  TM1R$StrikeZone[i] <- ifelse(TM1R$High[i] == 0 && TM1R$Low[i] == 0 && TM1R$Lefty[i] == 0 && TM1R$Righty[i] == 0, 1, 0)
  if(0.5 < TM1R$PlateLocSide[i] && TM1R$PlateLocSide[i] < 0.8333333) TM1R$CloseK[i] <- 1
  if(-0.5 > TM1R$PlateLocSide[i] && TM1R$PlateLocSide[i] > -0.8333333) TM1R$CloseK[i] <- 1
  if(0.8333333 < TM1R$PlateLocSide[i] && TM1R$PlateLocSide[i] < 1.1) TM1R$CloseB[i] <- 1
  if(-0.8333333 > TM1R$PlateLocSide[i] && TM1R$PlateLocSide[i] > -1.1) TM1R$CloseB[i] <- 1
  if(1 < TM1R$PlateLocHeight[i] && TM1R$PlateLocHeight[i] < 4) TM1R$CloseH[i] <- 1
}
```

```{r, echo=FALSE, include=FALSE}
TM1R$KcalledB <- rep(0, nrow(TM1R))
TM1R$BcalledK <- rep(0, nrow(TM1R))
TM1R$KcalledK <- rep(0, nrow(TM1R))
TM1R$BcalledB <- rep(0, nrow(TM1R))
TM1R$Incorrect <- rep(0, nrow(TM1R))
TM1R$Correct <- rep(0, nrow(TM1R))
for (i in 1:nrow(TM1R)) {
  TM1R$KcalledB[i] <- ifelse(TM1R$StrikeZone[i] == 1 && TM1R$PitchCall[i] == "BallCalled", 1, 0)
  TM1R$BcalledK[i] <- ifelse(TM1R$StrikeZone[i] == 0 && TM1R$PitchCall[i] == "StrikeCalled", 1, 0)
  TM1R$KcalledK[i] <- ifelse(TM1R$StrikeZone[i] == 1 && TM1R$PitchCall[i] == "StrikeCalled", 1, 0)
  TM1R$BcalledB[i] <- ifelse(TM1R$StrikeZone[i] == 0 && TM1R$PitchCall[i] == "BallCalled", 1, 0)
  if(TM1R$KcalledB[i] == 1) TM1R$Incorrect[i] <- 1
  if(TM1R$BcalledK[i] == 1) TM1R$Incorrect[i] <- 1
  if(TM1R$KcalledK[i] == 1) TM1R$Correct[i] <- 1
  if(TM1R$BcalledB[i] == 1) TM1R$Correct[i] <- 1
}
```

```{r, echo=FALSE, include=FALSE}
KBsum <- sum(TM1R$KcalledB)
BKsum <- sum(TM1R$BcalledK)
KKsum <- sum(TM1R$KcalledK)
BBsum <- sum(TM1R$BcalledB)
accurate <- KKsum + BBsum
inaccurate <- KBsum + BKsum
strikes <- KBsum + KKsum
balls <- BKsum + BBsum
accurate
inaccurate
total <- accurate + inaccurate
umpire <- matrix(c(KBsum, BKsum, inaccurate, (KKsum), BBsum, accurate, strikes, balls, total, round(KKsum/strikes, 3), round(BBsum/balls, 3), round(accurate/total, 3)), ncol = 3, byrow = TRUE)
colnames(umpire) <- c("Zone", "No Zone", "Total")
rownames(umpire) <- c("Incorrect", "Correct", "Total", "Accuracy")
```

Table showing umpire's accuracy:

```{r, echo=FALSE}
umpire
```

```{r, echo=FALSE, include=FALSE}
thislist <- 0
thislist2 <- 0
thislist3 <- 0
thislist4 <- 0
thislist5 <- 0
thislist6 <- 0
for (i in 1:nrow(TM1R)) {
  if(TM1R$Incorrect[i] == 1) thislist <- c(thislist, i)
  if(TM1R$KcalledB[i] == 1) thislist2 <- c(thislist2, i)
  if(TM1R$BcalledK[i] == 1) thislist3 <- c(thislist3, i)
  if(TM1R$Correct[i] == 1) thislist4 <- c(thislist4, i)
  if(TM1R$CloseK[i] == 1 && TM1R$KcalledK[i] == 1 && TM1R$CloseH[i] == 1) thislist5 <- c(thislist5, i)
  if(TM1R$CloseB[i] == 1 && TM1R$Correct[i] == 1 && TM1R$CloseH[i] == 1) thislist6 <- c(thislist6, i)
}
TMWrong <- TM1R[thislist[-1],]
TMKcalledB <- TM1R[thislist2[-1],]
TMBcalledK <- TM1R[thislist3[-1],]
TMCorrect <- TM1R[thislist4[-1],]
TMCloseK <- TM1R[thislist5[-1],]
TMCloseB <- TM1R[thislist6[-1],]
nrow(TMWrong)
nrow(TMKcalledB)
nrow(TMBcalledK)
nrow(TMCorrect)
nrow(TMCloseK)
nrow(TMCloseB)
```

```{r, echo=FALSE}
library(ggplot2)
ggplot(data = TMKcalledB, aes(PlateLocSide*-1, PlateLocHeight)) + geom_point(color = "orange") + geom_point(data = TMBcalledK, aes(PlateLocSide*-1, PlateLocHeight), color = "red") + geom_point(data = TMCloseK, aes(PlateLocSide*-1, PlateLocHeight), color = "blue") + geom_point(data = TMCloseB, aes(PlateLocSide*-1, PlateLocHeight), color = "green") + geom_vline(xintercept = -0.8333333) + geom_vline(xintercept = 0.8333333) + geom_hline(yintercept = 3.5) + geom_hline(yintercept = 1.5) + ggtitle("Behind Home View of Umpire's Close Calls") + xlab("") + ylab("") + theme(plot.title = element_text(hjust = 0.5))
```

```{r, echo=FALSE, include=FALSE}
#View(TMWrong)
thislist2 <- 0
for (i in 1:nrow(TMWrong)) {
  if(TMWrong$StrikeZone[i] == 0) thislist2 <- c(thislist2, i)
}
TMBalls <- TMWrong[thislist2[-1],]
#View(TMBalls)
missareaprop <- prop.table(c(sum(TMBalls$High), sum(TMBalls$Low), sum(TMBalls$Lefty), sum(TMBalls$Righty)))
missarea <- matrix(c(sum(TMBalls$High), sum(TMBalls$Low), sum(TMBalls$Lefty), sum(TMBalls$Righty), sum(c(TMBalls$High, TMBalls$Low, TMBalls$Lefty, TMBalls$Righty)), round(missareaprop[1], 3), round(missareaprop[2], 3), round(missareaprop[3], 3), round(missareaprop[4], 3), 1), nrow = 2, byrow = TRUE)
colnames(missarea) <- c("Up", "Down", "Lefty In", "Lefty Out", "Total")
rownames(missarea) <- c("Misses", "Proportion")
```

Location of missed calls:

```{r, echo=FALSE}
missarea
```

\pagebreak

# Umpire All

```{r, echo=FALSE, include=FALSE}
TM1$High <- rep(0, nrow(TM1))
TM1$Low <- rep(0, nrow(TM1))
TM1$Lefty <- rep(0, nrow(TM1))
TM1$Righty <- rep(0, nrow(TM1))
TM1$StrikeZone <- rep(0, nrow(TM1))
TM1$CloseK <- rep(0, nrow(TM1))
TM1$CloseB <- rep(0, nrow(TM1))
TM1$CloseH <- rep(0, nrow(TM1))
for (i in 1:nrow(TM1)) {
  TM1$High[i] <- ifelse(TM1$PlateLocHeight[i] > 3.5, 1, 0)
  TM1$Low[i] <- ifelse(TM1$PlateLocHeight[i] < 1.5, 1, 0)
  TM1$Lefty[i] <- ifelse(TM1$PlateLocSide[i] < -0.8333333, 1, 0)
  TM1$Righty[i] <- ifelse(TM1$PlateLocSide[i] > 0.8333333, 1, 0)
  TM1$StrikeZone[i] <- ifelse(TM1$High[i] == 0 && TM1$Low[i] == 0 && TM1$Lefty[i] == 0 && TM1$Righty[i] == 0, 1, 0)
  if(0.5 < TM1$PlateLocSide[i] && TM1$PlateLocSide[i] < 0.8333333) TM1$CloseK[i] <- 1
  if(-0.5 > TM1$PlateLocSide[i] && TM1$PlateLocSide[i] > -0.8333333) TM1$CloseK[i] <- 1
  if(0.8333333 < TM1$PlateLocSide[i] && TM1$PlateLocSide[i] < 1.1) TM1$CloseB[i] <- 1
  if(-0.8333333 > TM1$PlateLocSide[i] && TM1$PlateLocSide[i] > -1.1) TM1$CloseB[i] <- 1
  if(1 < TM1$PlateLocHeight[i] && TM1$PlateLocHeight[i] < 4) TM1$CloseH[i] <- 1
}
```

```{r, echo=FALSE, include=FALSE}
TM1$KcalledB <- rep(0, nrow(TM1))
TM1$BcalledK <- rep(0, nrow(TM1))
TM1$KcalledK <- rep(0, nrow(TM1))
TM1$BcalledB <- rep(0, nrow(TM1))
TM1$Incorrect <- rep(0, nrow(TM1))
TM1$Correct <- rep(0, nrow(TM1))
for (i in 1:nrow(TM1)) {
  TM1$KcalledB[i] <- ifelse(TM1$StrikeZone[i] == 1 && TM1$PitchCall[i] == "BallCalled", 1, 0)
  TM1$BcalledK[i] <- ifelse(TM1$StrikeZone[i] == 0 && TM1$PitchCall[i] == "StrikeCalled", 1, 0)
  TM1$KcalledK[i] <- ifelse(TM1$StrikeZone[i] == 1 && TM1$PitchCall[i] == "StrikeCalled", 1, 0)
  TM1$BcalledB[i] <- ifelse(TM1$StrikeZone[i] == 0 && TM1$PitchCall[i] == "BallCalled", 1, 0)
  if(TM1$KcalledB[i] == 1) TM1$Incorrect[i] <- 1
  if(TM1$BcalledK[i] == 1) TM1$Incorrect[i] <- 1
  if(TM1$KcalledK[i] == 1) TM1$Correct[i] <- 1
  if(TM1$BcalledB[i] == 1) TM1$Correct[i] <- 1
}
```

```{r, echo=FALSE, include=FALSE}
KBsum <- sum(TM1$KcalledB)
BKsum <- sum(TM1$BcalledK)
KKsum <- sum(TM1$KcalledK)
BBsum <- sum(TM1$BcalledB)
accurate <- KKsum + BBsum
inaccurate <- KBsum + BKsum
strikes <- KBsum + KKsum
balls <- BKsum + BBsum
accurate
inaccurate
total <- accurate + inaccurate
umpire <- matrix(c(KBsum, BKsum, inaccurate, (KKsum), BBsum, accurate, strikes, balls, total, round(KKsum/strikes, 3), round(BBsum/balls, 3), round(accurate/total, 3)), ncol = 3, byrow = TRUE)
colnames(umpire) <- c("Zone", "No Zone", "Total")
rownames(umpire) <- c("Incorrect", "Correct", "Total", "Accuracy")
```

Table showing umpire's accuracy:

```{r, echo=FALSE}
umpire
```

```{r, echo=FALSE, include=FALSE}
thislist <- 0
thislist2 <- 0
thislist3 <- 0
thislist4 <- 0
thislist5 <- 0
thislist6 <- 0
for (i in 1:nrow(TM1)) {
  if(TM1$Incorrect[i] == 1) thislist <- c(thislist, i)
  if(TM1$KcalledB[i] == 1) thislist2 <- c(thislist2, i)
  if(TM1$BcalledK[i] == 1) thislist3 <- c(thislist3, i)
  if(TM1$Correct[i] == 1) thislist4 <- c(thislist4, i)
  if(TM1$CloseK[i] == 1 && TM1$KcalledK[i] == 1 && TM1$CloseH[i] == 1) thislist5 <- c(thislist5, i)
  if(TM1$CloseB[i] == 1 && TM1$Correct[i] == 1 && TM1$CloseH[i] == 1) thislist6 <- c(thislist6, i)
}
TMWrong <- TM1[thislist[-1],]
TMKcalledB <- TM1[thislist2[-1],]
TMBcalledK <- TM1[thislist3[-1],]
TMCorrect <- TM1[thislist4[-1],]
TMCloseK <- TM1[thislist5[-1],]
TMCloseB <- TM1[thislist6[-1],]
nrow(TMWrong)
nrow(TMKcalledB)
nrow(TMBcalledK)
nrow(TMCorrect)
nrow(TMCloseK)
nrow(TMCloseB)
```

```{r, echo=FALSE}
library(ggplot2)
ggplot(data = TMKcalledB, aes(PlateLocSide*-1, PlateLocHeight)) + geom_point(color = "orange") + geom_point(data = TMBcalledK, aes(PlateLocSide*-1, PlateLocHeight), color = "red") + geom_point(data = TMCloseK, aes(PlateLocSide*-1, PlateLocHeight), color = "blue") + geom_point(data = TMCloseB, aes(PlateLocSide*-1, PlateLocHeight), color = "green") + geom_vline(xintercept = -0.8333333) + geom_vline(xintercept = 0.8333333) + geom_hline(yintercept = 3.5) + geom_hline(yintercept = 1.5) + ggtitle("Behind Home View of Umpire's Close Calls") + xlab("") + ylab("") + theme(plot.title = element_text(hjust = 0.5))
```

```{r, echo=FALSE, include=FALSE}
#View(TMWrong)
thislist2 <- 0
for (i in 1:nrow(TMWrong)) {
  if(TMWrong$StrikeZone[i] == 0) thislist2 <- c(thislist2, i)
}
TMBalls <- TMWrong[thislist2[-1],]
#View(TMBalls)
missareaprop <- prop.table(c(sum(TMBalls$High), sum(TMBalls$Low), sum(TMBalls$Lefty), sum(TMBalls$Righty)))
missarea <- matrix(c(sum(TMBalls$High), sum(TMBalls$Low), sum(TMBalls$Lefty), sum(TMBalls$Righty), sum(c(TMBalls$High, TMBalls$Low, TMBalls$Lefty, TMBalls$Righty)), round(missareaprop[1], 3), round(missareaprop[2], 3), round(missareaprop[3], 3), round(missareaprop[4], 3), 1), nrow = 2, byrow = TRUE)
colnames(missarea) <- c("Up", "Down", "Lefty In", "Righty In", "Total")
rownames(missarea) <- c("Misses", "Proportion")
```

Location of missed calls:

```{r, echo=FALSE}
missarea
```

\pagebreak

```{r, echo=FALSE, include=FALSE}
Ump1L <- Umpire[which(Umpire$PitcherTeam == "UCLA"),]
Ump1R <- Umpire[which(Umpire$PitcherTeam != "UCLA"),]
TM1L <- Ump1L[,c(22,41,42)]
TM1R <- Ump1R[,c(22,41,42)]
```

# Umpire for UCLA

```{r, echo=FALSE, include=FALSE}
table(is.na(TM1L))
names(TM1L) <- c("PitchCall", "PlateLocHeight", "PlateLocSide")
#View(TM1L)
```

```{r, echo=FALSE, include=FALSE}
TM1L$High <- rep(0, nrow(TM1L))
TM1L$Low <- rep(0, nrow(TM1L))
TM1L$Lefty <- rep(0, nrow(TM1L))
TM1L$Righty <- rep(0, nrow(TM1L))
TM1L$StrikeZone <- rep(0, nrow(TM1L))
TM1L$CloseK <- rep(0, nrow(TM1L))
TM1L$CloseB <- rep(0, nrow(TM1L))
TM1L$CloseH <- rep(0, nrow(TM1L))
for (i in 1:nrow(TM1L)) {
  TM1L$High[i] <- ifelse(TM1L$PlateLocHeight[i] > 3.5, 1, 0)
  TM1L$Low[i] <- ifelse(TM1L$PlateLocHeight[i] < 1.5, 1, 0)
  TM1L$Lefty[i] <- ifelse(TM1L$PlateLocSide[i] < -0.8333333, 1, 0)
  TM1L$Righty[i] <- ifelse(TM1L$PlateLocSide[i] > 0.8333333, 1, 0)
  TM1L$StrikeZone[i] <- ifelse(TM1L$High[i] == 0 && TM1L$Low[i] == 0 && TM1L$Lefty[i] == 0 && TM1L$Righty[i] == 0, 1, 0)
  if(0.5 < TM1L$PlateLocSide[i] && TM1L$PlateLocSide[i] < 0.8333333) TM1L$CloseK[i] <- 1
  if(-0.5 > TM1L$PlateLocSide[i] && TM1L$PlateLocSide[i] > -0.8333333) TM1L$CloseK[i] <- 1
  if(0.8333333 < TM1L$PlateLocSide[i] && TM1L$PlateLocSide[i] < 1.1) TM1L$CloseB[i] <- 1
  if(-0.8333333 > TM1L$PlateLocSide[i] && TM1L$PlateLocSide[i] > -1.1) TM1L$CloseB[i] <- 1
  if(1 < TM1L$PlateLocHeight[i] && TM1L$PlateLocHeight[i] < 4) TM1L$CloseH[i] <- 1
}
```

```{r, echo=FALSE, include=FALSE}
TM1L$KcalledB <- rep(0, nrow(TM1L))
TM1L$BcalledK <- rep(0, nrow(TM1L))
TM1L$KcalledK <- rep(0, nrow(TM1L))
TM1L$BcalledB <- rep(0, nrow(TM1L))
TM1L$Incorrect <- rep(0, nrow(TM1L))
TM1L$Correct <- rep(0, nrow(TM1L))
for (i in 1:nrow(TM1L)) {
  TM1L$KcalledB[i] <- ifelse(TM1L$StrikeZone[i] == 1 && TM1L$PitchCall[i] == "BallCalled", 1, 0)
  TM1L$BcalledK[i] <- ifelse(TM1L$StrikeZone[i] == 0 && TM1L$PitchCall[i] == "StrikeCalled", 1, 0)
  TM1L$KcalledK[i] <- ifelse(TM1L$StrikeZone[i] == 1 && TM1L$PitchCall[i] == "StrikeCalled", 1, 0)
  TM1L$BcalledB[i] <- ifelse(TM1L$StrikeZone[i] == 0 && TM1L$PitchCall[i] == "BallCalled", 1, 0)
  if(TM1L$KcalledB[i] == 1) TM1L$Incorrect[i] <- 1
  if(TM1L$BcalledK[i] == 1) TM1L$Incorrect[i] <- 1
  if(TM1L$KcalledK[i] == 1) TM1L$Correct[i] <- 1
  if(TM1L$BcalledB[i] == 1) TM1L$Correct[i] <- 1
}
```

```{r, echo=FALSE, include=FALSE}
KBsum <- sum(TM1L$KcalledB)
BKsum <- sum(TM1L$BcalledK)
KKsum <- sum(TM1L$KcalledK)
BBsum <- sum(TM1L$BcalledB)
accurate <- KKsum + BBsum
inaccurate <- KBsum + BKsum
strikes <- KBsum + KKsum
balls <- BKsum + BBsum
accurate
inaccurate
total <- accurate + inaccurate
umpire <- matrix(c(KBsum, BKsum, inaccurate, (KKsum), BBsum, accurate, strikes, balls, total, round(KKsum/strikes, 3), round(BBsum/balls, 3), round(accurate/total, 3)), ncol = 3, byrow = TRUE)
colnames(umpire) <- c("Zone", "No Zone", "Total")
rownames(umpire) <- c("Incorrect", "Correct", "Total", "Accuracy")
```

Table showing umpire's accuracy:

```{r, echo=FALSE}
umpire
```

```{r, echo=FALSE, include=FALSE}
thislist <- 0
thislist2 <- 0
thislist3 <- 0
thislist4 <- 0
thislist5 <- 0
thislist6 <- 0
for (i in 1:nrow(TM1L)) {
  if(TM1L$Incorrect[i] == 1) thislist <- c(thislist, i)
  if(TM1L$KcalledB[i] == 1) thislist2 <- c(thislist2, i)
  if(TM1L$BcalledK[i] == 1) thislist3 <- c(thislist3, i)
  if(TM1L$Correct[i] == 1) thislist4 <- c(thislist4, i)
  if(TM1L$CloseK[i] == 1 && TM1L$KcalledK[i] == 1 && TM1L$CloseH[i] == 1) thislist5 <- c(thislist5, i)
  if(TM1L$CloseB[i] == 1 && TM1L$Correct[i] == 1 && TM1L$CloseH[i] == 1) thislist6 <- c(thislist6, i)
}
TMWrong <- TM1L[thislist[-1],]
TMKcalledB <- TM1L[thislist2[-1],]
TMBcalledK <- TM1L[thislist3[-1],]
TMCorrect <- TM1L[thislist4[-1],]
TMCloseK <- TM1L[thislist5[-1],]
TMCloseB <- TM1L[thislist6[-1],]
nrow(TMWrong)
nrow(TMKcalledB)
nrow(TMBcalledK)
nrow(TMCorrect)
nrow(TMCloseK)
nrow(TMCloseB)
```

```{r, echo=FALSE}
library(ggplot2)
ggplot(data = TMKcalledB, aes(PlateLocSide*-1, PlateLocHeight)) + geom_point(color = "orange") + geom_point(data = TMBcalledK, aes(PlateLocSide*-1, PlateLocHeight), color = "red") + geom_point(data = TMCloseK, aes(PlateLocSide*-1, PlateLocHeight), color = "blue") + geom_point(data = TMCloseB, aes(PlateLocSide*-1, PlateLocHeight), color = "green") + geom_vline(xintercept = -0.8333333) + geom_vline(xintercept = 0.8333333) + geom_hline(yintercept = 3.5) + geom_hline(yintercept = 1.5) + ggtitle("Behind Home View of Umpire's Close Calls") + xlab("") + ylab("") + theme(plot.title = element_text(hjust = 0.5))
```

```{r, echo=FALSE, include=FALSE}
#View(TMWrong)
thislist2 <- 0
for (i in 1:nrow(TMWrong)) {
  if(TMWrong$StrikeZone[i] == 0) thislist2 <- c(thislist2, i)
}
TMBalls <- TMWrong[thislist2[-1],]
#View(TMBalls)
missareaprop <- prop.table(c(sum(TMBalls$High), sum(TMBalls$Low), sum(TMBalls$Lefty), sum(TMBalls$Righty)))
missarea <- matrix(c(sum(TMBalls$High), sum(TMBalls$Low), sum(TMBalls$Lefty), sum(TMBalls$Righty), sum(c(TMBalls$High, TMBalls$Low, TMBalls$Lefty, TMBalls$Righty)), round(missareaprop[1], 3), round(missareaprop[2], 3), round(missareaprop[3], 3), round(missareaprop[4], 3), 1), nrow = 2, byrow = TRUE)
colnames(missarea) <- c("Up", "Down", "Lefty In", "Lefty Out", "Total")
rownames(missarea) <- c("Misses", "Proportion")
```

Location of missed calls:

```{r, echo=FALSE}
missarea
```

\pagebreak

# Umpire for UC Riverside

```{r, echo=FALSE, include=FALSE}
table(is.na(TM1R))
names(TM1R) <- c("PitchCall", "PlateLocHeight", "PlateLocSide")
#View(TM1R)
```

```{r, echo=FALSE, include=FALSE}
TM1R$High <- rep(0, nrow(TM1R))
TM1R$Low <- rep(0, nrow(TM1R))
TM1R$Lefty <- rep(0, nrow(TM1R))
TM1R$Righty <- rep(0, nrow(TM1R))
TM1R$StrikeZone <- rep(0, nrow(TM1R))
TM1R$CloseK <- rep(0, nrow(TM1R))
TM1R$CloseB <- rep(0, nrow(TM1R))
TM1R$CloseH <- rep(0, nrow(TM1R))
for (i in 1:nrow(TM1R)) {
  TM1R$High[i] <- ifelse(TM1R$PlateLocHeight[i] > 3.5, 1, 0)
  TM1R$Low[i] <- ifelse(TM1R$PlateLocHeight[i] < 1.5, 1, 0)
  TM1R$Lefty[i] <- ifelse(TM1R$PlateLocSide[i] < -0.8333333, 1, 0)
  TM1R$Righty[i] <- ifelse(TM1R$PlateLocSide[i] > 0.8333333, 1, 0)
  TM1R$StrikeZone[i] <- ifelse(TM1R$High[i] == 0 && TM1R$Low[i] == 0 && TM1R$Lefty[i] == 0 && TM1R$Righty[i] == 0, 1, 0)
  if(0.5 < TM1R$PlateLocSide[i] && TM1R$PlateLocSide[i] < 0.8333333) TM1R$CloseK[i] <- 1
  if(-0.5 > TM1R$PlateLocSide[i] && TM1R$PlateLocSide[i] > -0.8333333) TM1R$CloseK[i] <- 1
  if(0.8333333 < TM1R$PlateLocSide[i] && TM1R$PlateLocSide[i] < 1.1) TM1R$CloseB[i] <- 1
  if(-0.8333333 > TM1R$PlateLocSide[i] && TM1R$PlateLocSide[i] > -1.1) TM1R$CloseB[i] <- 1
  if(1 < TM1R$PlateLocHeight[i] && TM1R$PlateLocHeight[i] < 4) TM1R$CloseH[i] <- 1
}
```

```{r, echo=FALSE, include=FALSE}
TM1R$KcalledB <- rep(0, nrow(TM1R))
TM1R$BcalledK <- rep(0, nrow(TM1R))
TM1R$KcalledK <- rep(0, nrow(TM1R))
TM1R$BcalledB <- rep(0, nrow(TM1R))
TM1R$Incorrect <- rep(0, nrow(TM1R))
TM1R$Correct <- rep(0, nrow(TM1R))
for (i in 1:nrow(TM1R)) {
  TM1R$KcalledB[i] <- ifelse(TM1R$StrikeZone[i] == 1 && TM1R$PitchCall[i] == "BallCalled", 1, 0)
  TM1R$BcalledK[i] <- ifelse(TM1R$StrikeZone[i] == 0 && TM1R$PitchCall[i] == "StrikeCalled", 1, 0)
  TM1R$KcalledK[i] <- ifelse(TM1R$StrikeZone[i] == 1 && TM1R$PitchCall[i] == "StrikeCalled", 1, 0)
  TM1R$BcalledB[i] <- ifelse(TM1R$StrikeZone[i] == 0 && TM1R$PitchCall[i] == "BallCalled", 1, 0)
  if(TM1R$KcalledB[i] == 1) TM1R$Incorrect[i] <- 1
  if(TM1R$BcalledK[i] == 1) TM1R$Incorrect[i] <- 1
  if(TM1R$KcalledK[i] == 1) TM1R$Correct[i] <- 1
  if(TM1R$BcalledB[i] == 1) TM1R$Correct[i] <- 1
}
```

```{r, echo=FALSE, include=FALSE}
KBsum <- sum(TM1R$KcalledB)
BKsum <- sum(TM1R$BcalledK)
KKsum <- sum(TM1R$KcalledK)
BBsum <- sum(TM1R$BcalledB)
accurate <- KKsum + BBsum
inaccurate <- KBsum + BKsum
strikes <- KBsum + KKsum
balls <- BKsum + BBsum
accurate
inaccurate
total <- accurate + inaccurate
umpire <- matrix(c(KBsum, BKsum, inaccurate, (KKsum), BBsum, accurate, strikes, balls, total, round(KKsum/strikes, 3), round(BBsum/balls, 3), round(accurate/total, 3)), ncol = 3, byrow = TRUE)
colnames(umpire) <- c("Zone", "No Zone", "Total")
rownames(umpire) <- c("Incorrect", "Correct", "Total", "Accuracy")
```

Table showing umpire's accuracy:

```{r, echo=FALSE}
umpire
```

```{r, echo=FALSE, include=FALSE}
thislist <- 0
thislist2 <- 0
thislist3 <- 0
thislist4 <- 0
thislist5 <- 0
thislist6 <- 0
for (i in 1:nrow(TM1R)) {
  if(TM1R$Incorrect[i] == 1) thislist <- c(thislist, i)
  if(TM1R$KcalledB[i] == 1) thislist2 <- c(thislist2, i)
  if(TM1R$BcalledK[i] == 1) thislist3 <- c(thislist3, i)
  if(TM1R$Correct[i] == 1) thislist4 <- c(thislist4, i)
  if(TM1R$CloseK[i] == 1 && TM1R$KcalledK[i] == 1 && TM1R$CloseH[i] == 1) thislist5 <- c(thislist5, i)
  if(TM1R$CloseB[i] == 1 && TM1R$Correct[i] == 1 && TM1R$CloseH[i] == 1) thislist6 <- c(thislist6, i)
}
TMWrong <- TM1R[thislist[-1],]
TMKcalledB <- TM1R[thislist2[-1],]
TMBcalledK <- TM1R[thislist3[-1],]
TMCorrect <- TM1R[thislist4[-1],]
TMCloseK <- TM1R[thislist5[-1],]
TMCloseB <- TM1R[thislist6[-1],]
nrow(TMWrong)
nrow(TMKcalledB)
nrow(TMBcalledK)
nrow(TMCorrect)
nrow(TMCloseK)
nrow(TMCloseB)
```

```{r, echo=FALSE}
library(ggplot2)
ggplot(data = TMKcalledB, aes(PlateLocSide*-1, PlateLocHeight)) + geom_point(color = "orange") + geom_point(data = TMBcalledK, aes(PlateLocSide*-1, PlateLocHeight), color = "red") + geom_point(data = TMCloseK, aes(PlateLocSide*-1, PlateLocHeight), color = "blue") + geom_point(data = TMCloseB, aes(PlateLocSide*-1, PlateLocHeight), color = "green") + geom_vline(xintercept = -0.8333333) + geom_vline(xintercept = 0.8333333) + geom_hline(yintercept = 3.5) + geom_hline(yintercept = 1.5) + ggtitle("Behind Home View of Umpire's Close Calls") + xlab("") + ylab("") + theme(plot.title = element_text(hjust = 0.5))
```

```{r, echo=FALSE, include=FALSE}
#View(TMWrong)
thislist2 <- 0
for (i in 1:nrow(TMWrong)) {
  if(TMWrong$StrikeZone[i] == 0) thislist2 <- c(thislist2, i)
}
TMBalls <- TMWrong[thislist2[-1],]
#View(TMBalls)
missareaprop <- prop.table(c(sum(TMBalls$High), sum(TMBalls$Low), sum(TMBalls$Lefty), sum(TMBalls$Righty)))
missarea <- matrix(c(sum(TMBalls$High), sum(TMBalls$Low), sum(TMBalls$Lefty), sum(TMBalls$Righty), sum(c(TMBalls$High, TMBalls$Low, TMBalls$Lefty, TMBalls$Righty)), round(missareaprop[1], 3), round(missareaprop[2], 3), round(missareaprop[3], 3), round(missareaprop[4], 3), 1), nrow = 2, byrow = TRUE)
colnames(missarea) <- c("Up", "Down", "Lefty In", "Lefty Out", "Total")
rownames(missarea) <- c("Misses", "Proportion")
```

Location of missed calls:

```{r, echo=FALSE}
missarea
```